Transforming Optimal Tetrahelices between the Boerdijk-Coxeter Helix and a Planar-faced Tetrahelix

### 2018-03-09 r1doc/RebuttalTetrahelixUntwistV2.tex

The inradius of the tetrahelix was also calculated to consider the insertion of material inside the
tetrahelix.

The equitetrabeam is introduced as a special case that the rail angle is zero. It is proposed that
transformation from tetrahelix to equitetrabeam is possible by changing the minimax ratio about
16\%.

Overall, this paper is acceptable, but requires some revision. The following includes some comments.

\subsection{Modification}
\begin{itemize}
\item
The sentences of this paper need to be compact. Please read several times and then clean
the sentences.
``without loss of generality'' $\rightarrow$ ``generally''
\highlighttext{The term ``without loss of generality'' is being used specifically as mathematical jargon\cite{wiki:wolog} to represent an assumption allowed in a proof because of symmetry or an ability to make
  a choice that does not change the validity of the proof.
  However, because this was unclear to the reviewer, in order to clarify this, I have added the word ``assume'' to the first use of the phrase ``without loss of generality'' and the phrase ``By symmetry'' to the second use.
  }

\item
  The explantaion for figure 8 can be erased by drawing the general case for figure 8.
  \highlighttext{Yes, you are correct, thank you, I have made the diagram (see \cref{fig:wobble}) more general and removed the
    disclaiming text.}
    \begin{figure}
     \centering
     \includegraphics[width=0.45\textwidth]{figures/WobbleDiagram2.png}
     \caption{Wobble Vectors from Non-Coincident Axes}
  \label{fig:wobble}
\end{figure}
  \item
    Instead of sentence starting to ‘we……’ , the passive sentence is recommended.
    \highlighttext{
      I believe editorial opinon is somewhat divided\cite{firstperson} on the use of the word ``we'' when it is used to mean ``the author and the reader together'' as I have used it. Most editors do not prefer passive sentences in general.
      Nonetheless, in deference to the reviewer, I have searched the paper for each use of the ``we'' and
      removed it in most, but not all cases.
      }
    \item 
 The following sentence is obscure. You'd better suggest a way to measure optimality using
 some kinematic indices :
\begin{quote}
 We have not yet proved that a two-class tetrahelix is optimal, but it suffices to show
that there exists such a better tetrahelix to show that different radii imply a suboptimal
tetrahelix.
\end{quote}

@@

   \highlighttext {
     In order to attempt to clarify the results of the paper I have added as the final subsection of the introduction the following summary of the contributions.
\subsection{Summary of Results}
The remainder of this  paper:
\begin{itemize}
\item Provides a new formulation for the BC helix that is more natural for engineers,
\item Defines a concept of minimum maximum edge-length optimality and proves that all
    optimal tetrahelices are in fact triple helices,
\item Provides formulae for construct optimal tetrahelices of different twists or for optimally
    transforming a
    robot from a twisted to a planar configuration,
\item Gives a formula for the inradius of an optimal tetrahelix,
\item Describes a completely planar tetrahlix (the \emph{equitetrabeam} useful as a structural beam or for apply standard robot gaits to a tetrahedral robot, and
\item Discusses the continuum of optimal tetrahelices between the BC Helix and equitetrabeam.
\end{itemize}
}

  \item
    I think the explaining optimization part should be revised. For a certain optimization problem, I think mathematics definition or algorithmic explanation can be helpful to understand the problem quickly. I think the author should refer problem definition standards from other optimization papers to revise this.
    \highlighttext{
      In order to clarify the ``Optimal Tetrahelices are Triple Helices'' section as requested,
      I have provided a mathematical description of the optimization, and a more mathematical
      description of the definition of the tetrahelix.
      }

  \item    
    In my opinion, the problem definition and proof of theorems looks being done based on personal experiences. I recommend using mathematical derivation or expression if possible.
    \highlighttext{
      I believe the theorems are all true (and verified by computer experimentation) and that the proofs
      are rigorous. However, in deference to the reviewer I have attempted to express parts of them
      more formally in several places. Unfortunately, it is beyond my ability to make them more completely formal
      in the space allowed in this paper. I hope readers will find them convincing at the available length.
      }

  \item    
    I think the demonstration by experiment can be helpful to understand the idea. Video attachment is recommended.
    \highlighttext{
I have included a public link to a video\cite{tetrahelixvideo} in the citations, and will upload the same video to the journal if appropriate.
\begin{quote}All math
developed here is available in JavaScript and demonstrated by an interactive
design website \url{https://pubinv.github.io/tetrahelix/}\cite{readtetrahelix}
\bf{and a video[9]},
from which figs. 1 and 2 and later figures in this paper 
are taken.      
\end{quote}
    }

@@

\end{enumerate}

Minors)

\begin{itemize}
  \item
    I am very confusing to the term ``An untwisted continuum'' and ``equitetrabeam.''
    \highlighttext{I have attempted to clarify this by adding the phrase:
      We call this the \emph{equitetrabeam}\textbf{, a portmanteau of ``equilateral tetrahedral beam''}.}
    Some other terminologies should be checked for 
“Conincident” should be “coincident”
\item
  Title is little bit not easy to be understood. “A continuum of optimal tetrahelices” can be changed to some other expression.
  \highlighttext{
    I have changed the title to:
 ``Transforming Optimal Tetrahelices between the Boerdijk-Coxeter Helix and a Planar-faced Tetrahelix''
}
\end{itemize}

### 2018-03-09 r1doc/TetrahelixUntwistV2.tex
getting close

\title{Optimal Tetrahelices Transforming between the Boerdijk-Coxeter Helix and a Planar-faced Tetrahelix}
\author{Robert L. Read
  \affiliation{
    Founder, Public Invention \\
    Austin, TX, 78704 \\
    Email: \href{mailto:read.robert@gmail.com}{read.robert@gmail.com} 
    }
}

@@

A BC helix does not rest stably on a plane. It is convenient to
be able to ``untwist'' it and to form a tetrahelix space frame that has a
flat planar surface. By making length changes in a certain way, a \highlighttext{tetrahelix untwists} to form a \emph{tetrabeam} which has planar faces
and has, for example, an equilateral triangular profile. This paper
develops the equations needed to untwist the tetrahelix. All math
developed here is available in JavaScript and demonstrated by an interactive
design website \url{https://pubinv.github.io/tetrahelix/}\cite{readtetrahelix}
\highlighttext{and a video\cite{readvideo}},
from which \cref{fig:closeup,fig:closeuporthog} and later figures in this paper 
are taken.

@@

  \Cref{fig:wobble} illustrates this situation. Like most diagrams, it is
  overspecific, in that the two circles are drawn of the same radius but \highlighttext{
    this proof does not depend on that.
  }
  The diagram represents the projection along the
  $z$-axis of a few points into the $XY$-plane.

  \begin{figure}
     \centering
     \includegraphics[width=0.45\textwidth]{figures/WobbleDiagram.png}
     \caption{Wobble Vectors from Non-Coincident Axes}
  \label{fig:wobble}
\end{figure}

>>>>

\title{Transforming Optimal Tetrahelices between the Boerdijk-Coxeter Helix and a Planar-faced Tetrahelix}
\author{Robert L. Read
  \affiliation{
    Founder, Public Invention \\
    Austin, TX, 78704 \\
    Email: \href{mailto:read.robert@gmail.com}{read.robert@gmail.com} 
    }
}

@@

A BC helix does not rest stably on a plane. It is convenient to
be able to ``untwist'' it and to form a tetrahelix space frame that has a
flat planar surface. By making length changes in a certain way, a \highlighttext{tetrahelix untwists} to form a \emph{tetrabeam} which has planar faces
and has, for example, an equilateral triangular profile. This paper
develops the equations needed to untwist the tetrahelix. All math
developed here is available in JavaScript and demonstrated by an interactive
design website \url{https://pubinv.github.io/tetrahelix/}\cite{readtetrahelix}
\highlighttext{and a video\cite{tetrahelixvideo}},
from which \cref{fig:closeup,fig:closeuporthog} and later figures in this paper 
are taken.

@@

  \Cref{fig:wobble} illustrates this situation.
  The diagram represents the projection along the
  $z$-axis of a few points into the $XY$-plane.

  \begin{figure}
     \centering
     \includegraphics[width=0.45\textwidth]{figures/WobbleDiagram2.png}
     \caption{Wobble Vectors from Non-Coincident Axes}
  \label{fig:wobble}
\end{figure}
